---
title: "reading_from_web"
author: "Tara"
date: "10/25/2021"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(httr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.clour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

sclae_colour_discrete = scale_color_viridis_d()
scale_fill_discrete = scale_fill_viridis_d
```

## NSDUH Data

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)

drug_use_df = 
  drug_use_html %>% 
  html_table() %>% 
  first() %>% 
  slice(-1)
```
This gets the tables from the web page^ can get first table.
This table has a footnote that's being put into the first row, so we slice out the first row. 
We can also make it a dataframe by putting df = 


## Star Wars

Getting some star wars data...

```{r}
sw_html = 
  read_html("https://www.imdb.com/list/ls070150896/")

sw_titles = 
  sw_html %>% 
  html_elements(".lister-item-header a") %>% 
  html_text()

sw_revenue = 
  sw_html %>% 
  html_elements(".text-small:nth-child(7) span:nth-child(5)") %>% 
  html_text()

sw_df = 
  tibble(
    title = sw_titles,
    revenue = sw_revenue
  )
```

Click SelectorGadget in your bookmarks bar and select the things you want, click again to deselect things you don't want. Copy/paste CCS Selector (lister-item-header a) into code.

##Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

dynamite_review_titles = 
  dynamite_html %>%
  html_elements(".a-text-bold span") %>%
  html_text()

dynamite_stars = 
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

dynamite_df = 
  tibble(
    titles = dynamite_review_titles,
    stars = dynamite_stars
  )
```



